---
title: "Johansen, VECM, Moving Average, Return"
output: html_document
---

```{r}
library(readr)
library(urca)
library(tseries)
library(vars)
library(lmtest)
library(TTR)
wticrude <- read_csv("G:/researchdata/wticrude.csv")
wtiheatingoil <- read_csv("G:/researchdata/wtiheatingoil.csv")
```
```{r}
ln.wticrude<-log(wticrude$price)
diff.wticrude<-diff(wticrude$price)
ln.diff.wticrude<-diff(ln.wticrude)
```
```{r}
perbarrel<-wtiheatingoil$price*42
ln.wtiheat<-log(perbarrel)
diff.wtiheat<-diff(perbarrel)
ln.diff.wtiheat<-diff(ln.wtiheat)
```

```{r}
Box.test(ln.diff.wticrude, lag = 500, type = "Ljung")##H0= stationary H1=non-stationary 
Box.test(ln.diff.wtiheat, lag = 3000, type = "Ljung")##H0= stationary H1=non-stationary 
```
## Johansen Cointegration test
```{r}
wticbine<-cbind(wticrude$price,wtiheatingoil$price)
diff.wticbine<-cbind(diff.wticrude,diff.wtiheat)
ln.wticbine<-cbind(ln.wticrude,ln.wtiheat)
ln.diff.wticbine<-cbind(ln.diff.wticrude,ln.diff.wtiheat)
```
### Johansen Cointegration test for ln.wti crude oil and heating oil(ln.wtinormal)(lag=2500).
```{r}
#ln.wtinormal<-ca.jo(ln.wticbine, type = "trace", ecdet = "none", K=2500, spec = "longrun")
#summary(ln.wtinormal)
```

```{r}
s=1.00*ln.wticrude-0.9705411*ln.wtiheat
plot(s, type="l")
adf.test(s)
```
### Johansen Cointegration test for ln.wti crude oil and heating oil(ln.wtinormal)(lag=50).
```{r}
ln.wtinormal50<-ca.jo(ln.wticbine, type = "trace", ecdet = "none", K=2, spec = "longrun")
summary(ln.wtinormal50)
```
### VECM
```{r}
vecm<-cajorls(ln.wtinormal50)
summary(vecm)
vecm
```
### Granger Causality test:
H0=Independent variable does not cause granger dependent variable
H1=Independent variable does cause granger dependent variable
```{r}
grangertest(ln.diff.wtiheat~ln.diff.wticrude, order=4)
```

```{r}
grangertest(ln.diff.wticrude~ln.diff.wtiheat, order=4)
```

```{r}
grangertest(ln.wticrude~ln.wtiheat, order=2)
```
```{r}
grangertest(ln.wtiheat~ln.wticrude, order=2)
```

```{r}
VARselect(ln.wticbine, lag.max = 100, type = "const")$selection
```
###Moving Average one week for log difference WTI Heating Oil
```{r}
ma1week<-EMA(ln.diff.wtiheat, n=5)
plot(ma1week, type = "l", xlim = c(1000,1500))
```
### Moving Average Four Weeks for log difference WTI Crude Oil
```{r}
ma4week<-EMA(ln.diff.wticrude, n = 20)
plot(ma4week, type = "l", xlim = c(1000,1500))
```
### Moving Average Signal
```{r}
signal<-ma4week-ma1week
plot(signal,type="l", xlim = c(1000,1500))
```
```{r}
library(methods)
```
### Round Up signals into 1 or -1
```{r}
signalround<-sign(signal)
```


```{r}
wtiheatpricebarrel<-wtiheatingoil$price*42
wtiheatprice<-wtiheatpricebarrel[1:8564]
wticrudeprice<-wticrude$price[1:8564]
signalfinal<-signalround[20:8583]
```

```{r}
combine<-cbind(wticrudeprice, wtiheatprice, signalfinal)
```
### Revised
```{r}
dailyreturn<-wticrudeprice*signalfinal*(-1)+wtiheatprice*signalfinal*0.9548025
bind<-cbind(ln.wticrude, ln.wtiheat, signalfinal, dailyreturn)
View(bind)
```

```{r}
sum(dailyreturn[1:365])
sum(dailyreturn[366:730])
sum(dailyreturn[731:1095])
sum(dailyreturn[1096:1460])
sum(dailyreturn[1461:1825])
```
```{r}
previous<-0
i<-1
priceleft<-0
priceright<-0
num<-0
annualreturn<-0
flag<-0
annualarray<-wticrudeprice*0
for (index in signalfinal){     ###在forloop情况下 if的loop里面是正常步骤 当需要辨别特殊步骤的时候 在else里展示
  if (index==previous){         ###index是signal里面的数 当index等于之前一项时 进行if部分 正常步骤
    num=num+1                  ###新的num就是在本身的num基础上加1
    priceleft=wticrudeprice[i]+priceleft  ### 将之前每一行符合标准的price叠加（原本等号左边是0，但是当i=1的时候 priceleft就有了值 从而实现累加
    priceright=wtiheatprice[i]*0.950073+priceright  ###同理上面
    #priceL[i] = wticrudeprice[i]   ###将上面累加结果进行保存
    #priceR[i] = wtiheatprice[i]
  }
    
  else {                        ### 当假设（index==previous）不成立的时候 即（index！=previous)
    #left=wticrudeprice[i]*num   ###则取之前完成的次数（num）乘以当前价格
    #right=wtiheatprice[i]*num
    #View(wticrudeprice[i])      ###同上  此时的num是从之前一步继承下来所以无需多虑
    #aboveleft=index*(priceleft-left)  ####计算一轮买卖差值
    #aboveright=index*(right-priceright)###同上
    #moneyreturn=aboveleft+aboveright
    
    if (num!=0){
      flag=flag+1  ##计数
      left=wticrudeprice[i]*num   ###则取之前完成的次数（num）乘以当前价格
      right=wtiheatprice[i]*num*0.950073   ###同上  此时的num是从之前一步继承下来所以无需多虑
      aboveleft=index*(priceleft-left)  ####计算一轮买卖差值
      aboveright=index*(right-priceright)###同上
      moneyreturn=aboveleft+aboveright
      if (index==1){    #???????
       cost=left+priceright
      }
      else{
       cost=right+priceleft
      }
      annualreturn=annualreturn+(1+moneyreturn/cost)**((num+1)/365)-1
      annualarray[i]<-annualreturn
      priceleft=0     ###参数归零
      priceright=0
      num=0
    }
    else {
          priceleft=wticrudeprice[i]     
          priceright=wtiheatprice[i]*0.950073
          num=1
      
    }
    #annualreturn<-(1+moneyreturn/cost)**((num+1)/365)-1  

  }
  i=i+1
  previous<-index
  
}
```
```{r}
a1<-annualarray[annualarray!=0]
View(a1)
plot(a1, type="l")
```
### Another Assumption
```{r}
previous<-0
i<-1
priceleft<-0
priceright<-0
num<-0
annualreturn<-0
flag<-0
annualarray<-wticrudeprice*0

for (index in signalfinal){     
  if (index==previous){         
    num=num+1                  
    priceleft=wticrudeprice[i]+priceleft   
    priceright=wtiheatprice[i]+priceright  
   
  }
    
  else {
    
    if (num!=0){
      flag=flag+1  
      left=wticrudeprice[i]*num   
      right=wtiheatprice[i]*num   
      aboveleft=index*(priceleft-left)  
      aboveright=index*(right-priceright)
      moneyreturn=aboveleft+aboveright
      if (index==1){    
       cost=left+priceright
      }
      else{
       cost=right+priceleft
      }
      annualreturn=annualreturn+(1+moneyreturn/cost)**(365/(num+1))-1
      annualarray[i]<-annualreturn
      priceleft=0     
      priceright=0
      num=0
    }
    else {
          priceleft=wticrudeprice[i]     
          priceright=wtiheatprice[i]
          num=1
      
    }
    #annualreturn<-(1+moneyreturn/cost)**((num+1)/365)-1  

  }
  i=i+1
  previous<-index
  
}
```

### Stationary Bootstrap
```{r}
tsbootstrap()
```